Collective excitations in competing phases in two and three dimensions

### 2023-12-14 paper/main.tex
as

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                                                  Abstract                                                 %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    We investigate the superconducting (SC), charge-density wave (CDW), and antiferromagnetic (AFM) phases 
    in the extended Hubbard model at zero temperature and half-filling.
    We employ the iterated equations of motion approach \cite{Kalthoff17,bleicker18} to compute the two-particle Green's functions and by extension, the corresponding spectral densities.
    This renders comprehensive analysis of the behaviour of collective excitations possible as the model's parameters are changed across phase transitions.
    We identify the well-known amplitude (Higgs) and phase (Leggett) modes within the superconducting phase and observe a similar excitation in the CDW phase which shifts towards zero energy as the system approaches the phase transition to the SC phase.
    In the CDW phase, close to the phase transition to the AFM phase, we find a collective mode that does not change significantly and another mode that becomes soft as the phase boundary is approached.
\end{abstract}

@@

Many recent experimental and theoretical studies examined the driven systems in the hope of inducing superconductivity 
\cite{Nicoletti14,Krull14,Moor14,Casandruc15,patel16,sentef17,Buenemann17}.
Other studies, focusing on equilibrium systems, 
investigated the phases and various quantities therein of the said model including various additional interactions with and without doping 
\cite{Micnas88,Micnas88b,Micnas89,Dzierzawa92,Kostyrko92,Eriksson95,Staudt00,Onari04,Toschi05,Brackett16,Paki19,romer20,Sushchyev22}.

@@

In this article, we will first employ a mean-field approximation to the interaction terms 
and then use the methodology from the so-called iterated equations of motion approach (iEoM),
which has already seen success in the handling of interaction quenches \cite{uhrig09,hamerla13,hamerla14,bleicker18}.
Here, one commutes operators from a suitable operator basis with the Hamiltonian and adds the newly occurring terms to it.
Naturally, a truncation is necessary for most practical applications, however, the approximation becomes better the more terms are included within the basis.
The functionality of this method has been compared to the density matrix formalism and has proved to be considerably more accurate \cite{Kalthoff17}.
Additionally, we will show an explicit way to obtain various Green's functions from the aforementioned methodology.
By extension, we also obtain the spectral functions of the investigated systems and discuss the excitations found therein.
The prominent examples in the SC phase are the well-known phase (Leggett) and amplitude (Higgs) modes \cite{Cea14,Krull16,Schwarz20,Fan22}.

@@

The Hamiltonian of the extended Hubbard model is given by
\begin{equation}
    \label{eqn:full_hamiltonian}
    \begin{aligned}
        H = &-t \sum_{\langle i, j \rangle, \sigma} \left( c_{i\sigma}^\dagger c_{j\sigma} + \text{h.c.} \right) 
        + \mu \sum_{i,\sigma} n_{i\sigma} \\
        &+ U \sum_{i} n_{i\uparrow} n_{i\downarrow} 
        + \frac{V}{2} \sum_{\langle i, j\rangle, \sigma} n_{i\sigma} n_{j\sigma}\,,
    \end{aligned}
\end{equation}
where $c_{i\sigma}^{(\dagger)}$ annihilates (creates) an electron with spin $\sigma$ on lattice site $i$ 
and $\langle i, j\rangle$ denotes the summation over next neighbours.
The parameters are the hopping amplitude $t$, the onsite interaction $U$, the intersite interaction $V$, and the chemical potential $\mu$.
Applying a Fourier-transformation into $k$-space yields the single-particle dispersion 
\begin{equation}
    \epsilon_0 (\vk) = -2t \sum_{\alpha=1}^D \cos(k_\alpha)\,,\quad k_\alpha \in [-\pi, \pi)\,,
\end{equation}
with the system's dimension $D$ and the dimensionless momentum $\vk$.

@@

In this article, we will be using the operator pseudo scalar product
\begin{equation}
\label{eqn:scalar_product}
    (A | B) \coloneqq  \langle [A^\dagger, B] \rangle\,,
\end{equation}
where the expectation values are taken with respect to the thermal equilibrium of the mean-field Hamiltonian \eqref{eqn:mf_hamiltonian}.
Note, that this is not a proper scalar product, as a norm defined using it can also be negative.
For example, assume that for some operator $A$
\begin{equation}
    ||A|| = (A | A) = \langle [A^\dagger, A] \rangle > 0\,,
\end{equation}
then
\begin{equation}
    ||A^\dagger|| = (A^\dagger | A^\dagger) = \langle [A, A^\dagger] \rangle = - ||A|| < 0\,.
\end{equation}
We will compute $\mM$ by commutating with the full Hubbard Hamiltonian \eqref{eqn:full_hamiltonian} enabling us to capture collective behaviour rather than the one particle dynamics given by the mean-field approximation.

@@

where $a_i$ and $b_i$ are the Lanczos coefficients \cite{PettiforRecursion,ViswanathRecursion}.
Obtaining a diagonal block of $\mathcal{G}$ is easily achieved by setting $\vec{b}(0) = \vec{a}(0)$.
Obtaining an off-diagonal block requires linear combinations in the form of \textcolor{red}{Ich bin damit nicht glücklich, da $\mathcal{G}$ ja eigentlich nicht hermitisch ist (wegen dem $z = \omega + i0^+$).
Das ist für die Ergebnisse völlig egal, da ich eh nur diagonale Blöcke betrachte, aber nunja...}
\begin{subequations}
    \begin{align}
        4 \Re [ \vec{a}^\dagger \mathcal{G} \vec{b} ] &= (\vec{a} + \vec{b})^\dagger \mathcal{G} (\vec{a} + \vec{b}) - (\vec{a} - \vec{b})^\dagger \mathcal{G} (\vec{a} - \vec{b}) \nonumber \\
            &= 2 \vec{a}^\dagger \mathcal{G} \vec{b} + 2 \vec{b}^\dagger \mathcal{G} \vec{a}\,, \\
        4i \Im [ \vec{a}^\dagger \mathcal{G} \vec{b} ] &= (\vec{a} + i \vec{b})^\dagger \mathcal{G} (\vec{a} + i \vec{b}) - (\vec{a} - i \vec{b})^\dagger \mathcal{G} (\vec{a} - i \vec{b}) \nonumber \\
            &= 2i \vec{a}^\dagger \mathcal{G} \vec{b} - 2i \vec{b}^\dagger \mathcal{G} \vec{a}\,.
    \end{align}
\end{subequations}
In the single-band case, the coefficients approach the limit
\begin{equation}
    \label{eqn:inf_lanczos}
    a_\infty = \frac{\omega_+ + \omega_-}{2}\text{  and  } b_\infty = \frac{\omega_+ - \omega_-}{4}\,,
\end{equation}
where $\omega_\pm$ represents the upper and lower band edge, respectively \cite{PettiforRecursion}.
This behaviour allows us to terminate the continued fraction, once the coefficients have converged close enough to these values, using the so-called square root terminator
\begin{equation}
    T(\omega) = \frac{1}{2b_\infty^2} \left( \omega - a_\infty \mp \sqrt{(\omega - a_\infty)^2 - 4 b_\infty^2} \right)\,,
\end{equation}
where the negative sign is to be chosen for $\omega - a_\infty > 2b_\infty$ and $|\omega - a_\infty| < 2b_\infty$ and the positive one otherwise.
It is to be noted, that the coefficients start to drop off from this limit as more and more Lanczos iterations are performed \cite{ViswanathRecursion}.
Therefore, we terminate the continued fraction with the aforementioned terminator at the coefficient pair that has the least deviation from $a_\infty$ and $b_\infty$.

@@

In this section, we will be investigating four different diagonal Green's functions $G_{AA^\dagger}(\omega + i0^+)$, namely with
\begin{subequations}
    \label{eqn:resolvent_bases}
    \begin{align}
        A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right)  
            = \int \dgamma \left( f_{\gamma} + f_{\gamma}^\dagger \right) \,,\\
        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right) = \int \dgamma \left( f_{\gamma} - f_{\gamma}^\dagger \right) \,,\\
        A_\text{CDW}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right) = \int \dgamma \left( g_{\gamma \up} + g_{\gamma \down} \right) \,,\\
        A_\text{AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) = \int \dgamma \left( g_{\gamma \up} - g_{\gamma \down} \right) \,,
    \end{align}
\end{subequations}
where $N$ is the number of lattice sites in the system. 
Each one of these operators generates a different kind of collective mode.
The first operator captures the amplitude mode of the $s$-wave superconducting state, while the second one catches the phase mode \cite{Fan22}.
The remaining two capture the collective behaviour of the CDW and AFM states, respectively.

@@

To begin, let us describe the the spectral function with respect to the operators above in the various phases.
A plot of those in the SC and CDW phase, close to the phase transition, is shown in \autoref{fig:resolvent_overview_SC}.
We chose $U=-2.5t$ and $V=\pm0.1t$ for both lattices.

@@

To further classify the aforementioned peaks that lie outside the two-particle continuum,
we turn towards the real part of the Green's function.
We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly $y = ax + b$ to obtain its power-law behaviour.
The real part is related to the imaginary part via the Kramers-Kronig relations.
Specifically, if the imaginary part is a $\delta$ distribution, the real part will be proportional to $1/\omega$, i.e., $a=-1$ and the peak has the weight $w_0 = \exp(b)$.
Furthermore, an exponent of $a=-2$ corresponds to the derivative of the $\delta$ distribution, i.e., $\delta'(\omega - \omega_0)$.

The plots for the phase peak and the CDW peak in the SC phase can be found in \autoref{sec:fit_greens_functions}.
The SC peak in the CDW phase behaves similarly to the latter and is therefore not shown explicitly.
We get a good agreement with the power-law behaviour near the peaks with the exponents $a=-2$ (phase) and $a=-1$ (CDW), respectively.
Therefore, we conclude that the CDW peak corresponds to a $\delta$ distribution, while the phase peak is its derivative.
Note, that the latter is located at $\omega=0$ of a perfectly asymmetrical bosonic spectral function and therefore must have 0 weight.
This is given here, because $\int \delta'(\omega) \mathrm{d}\omega = 0$.
The peak itself can be interpreted as two $\delta$ distributions at $0^\pm$.

Next, we will investigate the Higgs peak, this time around, turning towards the spectral function itself. 
We see in \autoref{fig:resolvent_overview_SC} that the Higgs and phase spectral functions become indistinguishable towards the upper half of the two-particle continuum.
Therefore, we interpret the latter as a background to the Higgs peak itself and compute the difference between both spectral functions.
Using the same methodology as before we obtain that the exponent is $a\approx-0.5$, indicating that the peak behaves as $1 / \sqrt{\omega - \omega_0}$.

Lastly, we investigate the same spectral functions close to the AFM-CDW phase transition, depicted in \autoref{fig:resolvent_overview_AFM}.
We choose $V=1t$ for both lattices and $U=zV \pm 0.1t$, where $z$ is the coordination number.
Again, the both SC-related spectral functions are identical in both the CDW and AFM phase.
Within the continuum their weight is shifted towards the upper edge and on the square lattice only, there is a peak above the continuum.
In the AFM phase, both the CDW and AFM spectral functions have a peak close, but yet below, the two-particle continuum.
The AFM peak is at a lower energy than the CDW one.
In the CDW phase, this behaviour is reversed, i.e., the CDW peak lies lower.
Using the same analysis as before, we conclude that each of these peaks is a $\delta$-peak.

@@

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw_position.pdf}
    \caption{The upper panels show double logarithmic plots of the positions $\omega_0$ of the SC peak in the CDW phases while the lower panels show their respective weights $w_0 = e^{b}$.
    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5$.
    The fits are linear, i.e., $y(V) = c \ln(V/t) + d$, and the parameters are printed on the individual panels.}
    \label{fig:sc_in_cdw_behaviour}
\end{figure*}

With the prevalent peaks discussed, we turn towards their behaviour as the system approaches the phase transition at $V=0$.
\textcolor{red}{TODO; weiter beschreiben}

@@

Numerically, we can compute the matrix elements like this
\begin{align}
    (A_i | A_j) &= \frac{(\Delta \gamma)^2}{N} \sum_{\vk \vl} h(\gamma_i - \hat{\gamma}(\vk)) h(\gamma_j - \hat{\gamma}(\vl)) (A_{\vk} | A_{\vl})\,.
\end{align}
Here, all expression are finite numbers and do not require further treatment.
Mutatis mutandis, one obtains a similar expression for $(A_i | [H, A_j])$.
Additionally note, that the expressions $(A_{\vk} | A_{\vl})$ and $(A_{\vk} | [H, A_{\vl}])$ can be reduced to sums of terms that are proportional to $\gamma_i$ or $\gamma_j$, respectively.
Therefore, it is not necessary to implement any sort of momentum space computations.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                                                  Abstract                                                 %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    We investigate the superconducting (SC), charge-density wave (CDW), and antiferromagnetic (AFM) phases 
    in the extended Hubbard model at zero temperature and half-filling.
    We employ the iterated equations of motion approach \cite{Kalthoff17,bleicker18} to compute the two-particle Green's functions and by extension, the corresponding spectral densities.
    This renders comprehensive analysis of the behavior of collective excitations possible as the model's parameters are changed across phase transitions.
    We identify the well-known amplitude (Higgs) and phase (Leggett) modes within the superconducting phase and observe a similar excitation in the CDW phase which shifts towards zero energy as the system approaches the phase transition to the SC phase.
    In the CDW phase, close to the phase transition to the AFM phase, we find a collective mode that does not change significantly and another mode that becomes soft as the phase boundary is approached.
\end{abstract}

@@

Many recent experimental and theoretical studies examined the driven systems in the hope of inducing superconductivity 
\cite{Volkov73,Yuzbashyan05,Yuzbashyan06,Nicoletti14,Krull14,Moor14,Casandruc15,patel16,sentef17,Buenemann17}.
Other studies, focusing on equilibrium systems, 
investigated the phases and various quantities therein of the said model including various additional interactions with and without doping 
\cite{Micnas88,Micnas88b,Micnas89,Dzierzawa92,Kostyrko92,Eriksson95,Staudt00,Onari04,Toschi05,Brackett16,Paki19,romer20,Sushchyev22}.

@@

In this article, we will first employ a mean-field approximation to the interaction terms 
and then use the methodology from the so-called iterated equations of motion approach (iEoM),
which has already seen success in the handling of interaction quenches \cite{uhrig09,hamerla13,hamerla14,bleicker18}.
Here, one commutes operators from a suitable operator basis with the Hamiltonian and adds the newly occurring terms to it.
Naturally, a truncation is necessary for most practical applications, however, the approximation becomes better the more terms are included within the basis.
The functionality of this method has been compared to the density matrix formalism and has proved to be considerably more accurate \cite{Kalthoff17}.
Additionally, we will show an explicit way to obtain various Green's functions from the aforementioned methodology.
By extension, we also obtain the spectral functions of the investigated systems and discuss the excitations found therein.
The prominent examples in the SC phase are the well-known phase (Leggett) and amplitude (Higgs) modes \cite{Cea14,Tsuji15,Krull16,Schwarz20,Fan22}.
The former is located at zero energy as our model describes neutral superfluids.
The latter is found at the lower edge of the two-particle continuum.

@@

The Hamiltonian of the extended Hubbard model is given by
\begin{equation}
    \label{eqn:full_hamiltonian}
    \begin{aligned}
        H = &-t \sum_{\langle i, j \rangle, \sigma} \left( c_{i\sigma}^\dagger c_{j\sigma} + \text{h.c.} \right) 
        + \mu \sum_{i,\sigma} n_{i\sigma} \\
        &+ U \sum_{i} n_{i\uparrow} n_{i\downarrow} 
        + \frac{V}{2} \sum_{\langle i, j\rangle, \sigma} n_{i\sigma} n_{j\sigma}\,,
    \end{aligned}
\end{equation}
where $c_{i\sigma}^{(\dagger)}$ annihilates (creates) an electron with spin $\sigma$ on lattice site $i$ 
and $\langle i, j\rangle$ denotes the summation over the next neighbors.
The parameters are the hopping amplitude $t$, the onsite interaction $U$, the intersite interaction $V$, and the chemical potential $\mu$.
Applying a Fourier transform into $k$ space yields the single-particle dispersion 
\begin{equation}
    \epsilon_0 (\vk) = -2t \sum_{\alpha=1}^D \cos(k_\alpha)\,,\quad k_\alpha \in [-\pi, \pi)\,,
\end{equation}
with the system's dimension $D$ and the dimensionless momentum $\vk$.

@@

In this article, we will be using the operator pseudo scalar product
\begin{equation}
\label{eqn:scalar_product}
    (A | B) \coloneqq  \langle [A^\dagger, B] \rangle\,,
\end{equation}
where the expectation values are taken with respect to the thermal equilibrium of the mean-field Hamiltonian \eqref{eqn:mf_hamiltonian}.
Note, that this is not a proper scalar product, as a norm defined using it can also be negative.
For example, assume that for some operator $A$
\begin{equation}
    ||A|| = (A | A) = \langle [A^\dagger, A] \rangle > 0\,,
\end{equation}
then
\begin{equation}
    ||A^\dagger|| = (A^\dagger | A^\dagger) = \langle [A, A^\dagger] \rangle = - ||A|| < 0\,.
\end{equation}
We will compute $\mM$ by commutating with the full Hubbard Hamiltonian \eqref{eqn:full_hamiltonian} enabling us to capture collective behavior rather than the one particle dynamics given by the mean-field approximation.

@@

where $a_i$ and $b_i$ are the Lanczos coefficients \cite{PettiforRecursion,ViswanathRecursion}.
Obtaining a diagonal block of $\mathcal{G}$ is easily achieved by setting $\vec{b}(0) = \vec{a}(0)$.
Obtaining an off-diagonal block requires linear combinations in the form of 
\begin{align}
    \vec{a}^\dagger \mathcal{G} \vec{b} &= \frac{1}{4} \Big\{ 
        \underbrace{\left[ (\vec{a} + \vec{b})^\dagger \mathcal{G} (\vec{a} + \vec{b}) - (\vec{a} - \vec{b})^\dagger \mathcal{G} (\vec{a} - \vec{b}) \right]}_{ = 2 \vec{a}^\dagger \mathcal{G} \vec{b} + 2 \vec{b}^\dagger \mathcal{G} \vec{a}} \\
    &-i \underbrace{\left[ (\vec{a} + i \vec{b})^\dagger \mathcal{G} (\vec{a} + i \vec{b}) - (\vec{a} - i \vec{b})^\dagger \mathcal{G} (\vec{a} - i \vec{b}) \right]}_{= 2i \vec{a}^\dagger \mathcal{G} \vec{b} - 2i \vec{b}^\dagger \mathcal{G} \vec{a}} \Big\}\,, \nonumber
\end{align}
i.e., one computes the four diagonal blocks and then simply adds them as described above.

In the single-band case, the coefficients approach the limit
\begin{equation}
    \label{eqn:inf_lanczos}
    a_\infty = \frac{\omega_+ + \omega_-}{2}\text{  and  } b_\infty = \frac{\omega_+ - \omega_-}{4}\,,
\end{equation}
where $\omega_\pm$ represents the upper and lower band edge, respectively \cite{PettiforRecursion}.
This behavior allows us to terminate the continued fraction, once the coefficients have converged close enough to these values, using the so-called square root terminator
\begin{equation}
    T(\omega) = \frac{1}{2b_\infty^2} \left( \omega - a_\infty \mp \sqrt{(\omega - a_\infty)^2 - 4 b_\infty^2} \right)\,,
\end{equation}
where the negative sign is to be chosen for $\omega - a_\infty > 2b_\infty$ and $|\omega - a_\infty| < 2b_\infty$ and the positive one otherwise.
It is to be noted, that the coefficients start to drop off from this limit as more and more Lanczos iterations are performed \cite{ViswanathRecursion}.
Therefore, we terminate the continued fraction with the aforementioned terminator at the coefficient pair that has the least deviation from $a_\infty$ and $b_\infty$.

@@

In this section, we will be investigating four different diagonal Green's functions $G_{AA^\dagger}(\omega + i0^+)$, namely with
\begin{subequations}
    \label{eqn:resolvent_bases}
    \begin{align}
        A_\text{Higgs} &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} + f_{\vk}^\dagger \right)  
            = \int \dgamma \left( f_{\gamma} + f_{\gamma}^\dagger \right) \,,\\
        A_\text{Phase} &= \frac{i}{\sqrt{N}} \sum_{\vk} \left( f_{\vk} - f_{\vk}^\dagger \right) = \int \dgamma \left( f_{\gamma} - f_{\gamma}^\dagger \right) \,,\\
        A_\text{CDW}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} + g_{\vk \down} \right) = \int \dgamma \left( g_{\gamma \up} + g_{\gamma \down} \right) \,,\\
        A_\text{AFM}   &= \frac{1}{\sqrt{N}} \sum_{\vk} \left( g_{\vk \up} - g_{\vk \down} \right) = \int \dgamma \left( g_{\gamma \up} - g_{\gamma \down} \right) \,,
    \end{align}
\end{subequations}
where $N$ is the number of lattice sites in the system. 
Each one of these operators generates a different kind of collective mode.
The first operator captures the amplitude mode of the $s$-wave superconducting state, while the second one catches the phase mode \cite{Fan22}.
The remaining two capture the collective behavior of the CDW and AFM states, respectively.

@@

To begin, let us describe the spectral function with respect to the operators above in the various phases.
A plot of those in the SC and CDW phase, close to the phase transition, is shown in \autoref{fig:resolvent_overview_SC}.
We chose $U=-2.5t$ and $V=\pm0.1t$ for both lattices.

@@

To further classify the aforementioned peaks that lie outside the two-particle continuum,
we turn towards the real part of the Green's function.
We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly $y = ax + b$ to obtain its power-law behavior.
The real part is related to the imaginary part via the Kramers-Kronig relations.
Specifically, if the imaginary part is a $\delta$ distribution, the real part will be proportional to $1/\omega$, i.e., $a=-1$ and the peak has the weight $w_0 = \exp(b)$.
Furthermore, an exponent of $a=-2$ corresponds to the derivative of the $\delta$ distribution, i.e., $\delta'(\omega - \omega_0)$.

The plots for the phase peak and the CDW peak in the SC phase can be found in \autoref{sec:fit_greens_functions}.
The SC peak in the CDW phase behaves similarly to the latter and is therefore not shown explicitly.
We get a good agreement with the power-law behavior near the peaks with the exponents $a=-2$ (phase) and $a=-1$ (CDW), respectively.
Therefore, we conclude that the CDW peak corresponds to a $\delta$ distribution, while the phase peak is its derivative.
Note, that the latter is located at $\omega=0$ of a perfectly asymmetrical bosonic spectral function and therefore must have 0 weight.
This is given here, because $\int \delta'(\omega) \mathrm{d}\omega = 0$.
The peak itself can be interpreted as two $\delta$ distributions at $0^\pm$.

Next, we will investigate the Higgs peak, this time around, turning toward the spectral function itself. 
We see in \autoref{fig:resolvent_overview_SC} that the Higgs and phase spectral functions become indistinguishable towards the upper half of the two-particle continuum.
Therefore, we interpret the latter as a background to the Higgs peak itself and compute the difference between both spectral functions.
Using the same methodology as before we obtain that the exponent is $a\approx-0.5$, indicating that the peak behaves as $1 / \sqrt{\omega - \omega_0}$.

Lastly, we investigate the same spectral functions close to the AFM-CDW phase transition, depicted in \autoref{fig:resolvent_overview_AFM}.
We choose $V=1t$ for both lattices and $U=zV \pm 0.1t$, where $z$ is the coordination number.
Again, both SC-related spectral functions are identical in both the CDW and AFM phases.
Within the continuum their weight is shifted towards the upper edge and on the square lattice only, there is a peak above the continuum.
In the AFM phase, both the CDW and AFM spectral functions have a peak close, but yet below, the two-particle continuum.
The AFM peak is at a lower energy than the CDW one.
In the CDW phase, this behavior is reversed, i.e., the CDW peak lies lower.
Using the same analysis as before, we conclude that each of these peaks is a $\delta$ peak.

@@

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw_position.pdf}
    \caption{The upper panels show double logarithmic plots of the positions $\omega_0$ of the SC peak in the CDW phases while the lower panels show their respective weights $w_0 = e^{b}$.
    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5$.
    The fits are linear, i.e., $y(V) = c \ln(V/t) + d$, and the parameters are printed on the individual panels.}
    \label{fig:sc_in_cdw_behavior}
\end{figure*}

With the prevalent peaks discussed, we turn towards their behavior as the system approaches the phase transition at $V=0$.
\textcolor{red}{TODO; weiter beschreiben}

@@

Numerically, we can compute the matrix elements like this
\begin{align}
    (A_i | A_j) &= \frac{(\Delta \gamma)^2}{N} \sum_{\vk \vl} h(\gamma_i - \hat{\gamma}(\vk)) h(\gamma_j - \hat{\gamma}(\vl)) (A_{\vk} | A_{\vl})\,.
\end{align}
Here, all expressions are finite numbers and do not require further treatment.
Mutatis mutandis, one obtains a similar expression for $(A_i | [H, A_j])$.
Additionally, note, that the expressions $(A_{\vk} | A_{\vl})$ and $(A_{\vk} | [H, A_{\vl}])$ can be reduced to sums of terms that are proportional to $\gamma_i$ or $\gamma_j$, respectively.
Therefore, it is not necessary to implement any sort of momentum space computations.
